A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-11-11 jour/jour.tex
Minor

For each goal in each formalization, we used Sledgehammer to select either 16 or
256~lemmas, which were monomorphized and translated to SMT-LIB~2 along with the
goal. The resulting problem was given to the
development version of CVC4 (\textbf{TODO: which revision?}) %AJR : version is from September 15 2015, git doesn't give nice revision numbers unfortunately
and to
Z3 4.3.2 %(\textbf{TODO: really?}) AJR : yes
for comparison, each running for
up to 60~s on the StarExec cluster
\cite{stump-et-al-2014-starexec}.
Problems not involving any (co)datatypes were left out.
Due to the lack of machinery in Isabelle for parsing CVC4 proofs and
reconstructing inferences about (co)datatypes, the solvers are trusted
as oracles. % in these experiments.
%Z3 is included for comparison.

>>>>

For each goal in each formalization, we used Sledgehammer to select either 16 or
256~lemmas, which were monomorphized and translated to SMT-LIB~2 along with the
goal. The resulting problem was given to the
development version (from 15 September 2015) of CVC4 %AJR : version is from September 15 2015, git doesn't give nice revision numbers unfortunately
and to
Z3 4.3.2 %(\textbf{TODO: really?}) AJR : yes
for comparison, each running for
up to 60~s on the StarExec cluster
\cite{stump-et-al-2014-starexec}.
Problems not involving any (co)datatypes were left out.
Due to the lack of machinery in Isabelle for parsing CVC4 proofs and
reconstructing inferences about (co)datatypes, the solvers are trusted
as oracles. % in these experiments.
%Z3 is included for comparison.
